Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation--extrapolation capacity validation

### 2022-10-14 Article.tex
Clean directories and tracked files

\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{amssymb}

@@

% specify here the journal
\journal{NAME OF THE JOURNAL}

@@

\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
\newcommand{\dotp}{\boldsymbol{\cdot}}
\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
\newcommand{\ERMS}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\sigmoid}{sig}

% Redefine the esvector shape to remove overlapping
\usepackage{esvect}
\def\traitfill@#1#2#3#4{%
  $\m@th\mkern2mu\relax#4#1\mkern-1.5mu %on met \relbaredd au d\'ebut
   \cleaders\hbox{$#4\mkern-0.3mu#2\mkern-0.3mu$}\hfill %remplit avec relbareda
   \mkern-1.5mu#3$%
}
\renewcommand{\overrightarrow}{\vv}

\begin{document}

\begin{frontmatter}{}

\title{TITLE}

\author[LGP]{Olivier Pantalé \corref{cor1}}

\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

\author[LGP]{AUTHOR 2}

\author[LGP]{AUTHOR 3}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}

\begin{abstract}
ABSTRACT
\end{abstract}
\begin{keyword}
KEY1 \sep KEY2 \sep KEY3 \sep KEY4 \sep KEY5
\end{keyword}

\end{frontmatter}{}

\section{SECTION 1\label{sec:SECTION1}}

BLA BLA \cite{mime}

\section{SECTION 2\label{sec:SECTION2}}

BLA BLA

\section{SECTION 3\label{sec:SECTION3}}
BLA BLA

\bibliographystyle{elsarticle-num}
\addcontentsline{toc}{section}{\refname}
\bibliography{bibtex}

>>>>

% !TeX encoding = UTF-8
\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage[colorlinks = true]{hyperref}

@@

% specify here the journal
\journal{International Journal of Mechanical Sciences}

@@

%\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
%\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
%\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
%\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
\newcommand{\dotp}{\boldsymbol{\cdot}}
%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
%\newcommand{\ERMS}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\R}{\text{R}}
%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
%\DeclareMathOperator{\sech}{sech}
%\DeclareMathOperator{\sigmoid}{sig}

\usepackage{esvect}
% Redefine the esvector shape to remove overlapping
\def\traitfill@#1#2#3#4{%
  $\m@th\mkern2mu\relax#4#1\mkern-1.5mu %on met \relbaredd au d\'ebut
   \cleaders\hbox{$#4\mkern-0.3mu#2\mkern-0.3mu$}\hfill %remplit avec relbareda
   \mkern-1.5mu#3$%
}
\renewcommand{\overrightarrow}{\vv}

\begin{document}
\begin{frontmatter}

\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation--extrapolation capacity validation}

\author[LGP]{Pierre Tize Mha}
\author[ETS]{Prashant Dhondapure}
\author[LGP]{Amèvi Tongne}
\author[ETS]{Mohammad Jahazi}
\author[LGP]{Olivier Pantalé \corref{cor1}}
\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
\address[ETS]{Écolde de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}

\begin{abstract}
The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$ ) and temperatures ($1050^\circ\text{C} -1250^\circ$C ). Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy. Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model. These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $AARE$ and the Root Mean Square Error ($RMSE$). From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy. For the strain rate ($\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050^\circ$C and $1100^\circ$C  while in the case of the PTM model, the strain rate  ($\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$) is not well described. This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high. Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot{\varepsilon}^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$). The results of the ANN model show a very good agreement between the predictions and the experiment. This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction. To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.  
\end{abstract}

\begin{keyword}
Zerilli--Armstrong flow law \sep Constitutive behavior \sep Arhenius--flow law \sep Hansel--Spittel flow law \sep Johnson--Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
\end{keyword}

\end{frontmatter}
\linenumbers

%--------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%--------------------------------------------------------------------------
Continuous casting and rolling mechanisms are an integral part of the technological methods of medium deformation through a continuous water-cooled crystalliser before entering a rolling mill. Some of the advantages of this method are increased metal yield, energy saving, improved quality of continuous casting and easier mechanisation and automation . Deformation being a very complex process involving both elastic and plastic deformation, is accompanied by high temperatures, high strain rates and complex and variable friction conditions \cite{he2013comparative}. However, a quantitative study and analysis of the deformation mechanism does not provide accurate analytical solutions . Moreover, conducting an experiment is not only time-consuming but also requires a high level of funding \cite{changizian2012high}. To mitigate these two factors (to name but a few), the Finite Element Method (FEM) is widely used in the analysis and optimisation of process parameters of various materials . FEM effectively compensates for the shortcomings of the analytical and experimental methods and plays an important role in the correct formulation of technological parameters, the improvement of product quality and the in-depth knowledge of the deformation mechanism. For example FEM has been widely used to simulate and analyse steel hot forming processes, such as forging, rolling, extrusion and casting but the accuracy of the numerical solution provided by FEM for this type of analysis strongly depends  on the accuracy of the constitutive equation of the concerned material \cite{qin2010modeling, mandal2009constitutive, ji2018constitutive}.

Indeed, hot forming processes are an essential step in the manufacturing of mechanical components and directly affect the ﬁnal quality of the products such as microstructure and mechanical properties \cite{ashtiani2012constitutive}. Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallisation), which very often occur during hot working, influence the quality of the deformation of materials. The complexity of the deformation behavior, however, leads to the fact that the deformation can only be calculated accurately by using a computer code to model the response of the material under the specified loading conditions. To this end, a mathematical formulation is often used to represent the flow behavior of materials in a form that can be used in finite element software \cite{lin2008prediction,wu2012flow}.

Based on a thorough search of the literature many researchers have tried to predict the mechanical behavior of materials under hot working conditions using constitutive models. Therefore, various constitutive equations have been proposed to describe the flow behavior including phenomenological, physical and artiﬁcial neural network (ANN) models \cite{lin2011critical,shin2010phenomenological,rusinek2010thermo}. As for the semi-empirical models, they try to be at the border between the empirical and physical models. Among a large number of models, the Johnson--Cook (JC) \cite{Johnson-1983-Constitutive, Johnson-1985-Fracture} and the Zerilli--Armstrong (ZA) \cite{Zerilli-1987-Dislocation} models are the best known and available in finite element codes. The JC model is widely used because it is simple to use and has fewer constants to be determined \cite{Khan-2004-Quasi-static, NematNasser-2003-Thermomechanical}. However, this model, in its original state, contains some problems related to the phenomena describing the behavior of the material. We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021-Modified-JC}. To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998-Revised-JC, Vural-2003-Large, Lin-2010-Modified-JC, Lin-2012-Phenomenological, Li-2013-Modified-JC, Zhou-2019-Research, Zhang-2015-Modified-JC}. According to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988-Evaluation, Voyiadjis-2005-Microstructural, Dey-2007-Influence}. However, the drawbacks of this model are related to the temperature limit value of the test. Indeed, this model applies only to low strain rates and for temperatures limited to $0.6~T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005-Strain, Lee-2005-Strain, Chen-2007-Comparative, Lee-2006-Effects}. Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009-Thermo-viscoplastic}. In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{Nemat-2004-Plasticity, Lennon-2004-Influence, Muralli-2017-Performance, Cheng-2021-Modified-ZA, Muralli-2021-Finite}.
The hyperbolic sine Arrhenius-type constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the microstructure of the studied material because   this model allows to estimate the deformation energy of the material \cite{jonas1969strength,zhang2012effect,mostafaei2012hot}. Its original formulation has been revised several times in order to properly describe the obtained experimental behavior. In order to increase the accuracy of the model, the effects of strain \cite{slooff2007constitutive, li2012flow, xu2013constitutive}, strain rate \cite{lin2008constitutive, mandal2009constitutive} have been considered by several researchers. For example, Sloof \eal \cite{slooff2007constitutive} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that their model could predict the high temperature flow behavior of a magnesium alloy. Lin \eal \cite{lin2008constitutive}, on the other hand, modified the model by introducing a strain rate compensation factor.

The method based on artiﬁcial neural networks is an approach to predict the deformation behavior of materials under different conditions. ANN is in fact a method originally developed to simulate the biological processes of the human brain. And therefore it is not necessary to formulate a mathematical expresson and identify these parameters for this kind of model. The response of the deformation behavior of materials is highly non-linear at high temperatures, and many factors affecting the deformation behavior of materials are also non-linear; this makes the accuracy of the flow stress predicted by regression methods and the appropriate range is limited. Faced with these limitations, ANN models are therefore of interest.  Indeed, ANNs are particularly suited to deal with complex and non-linear relationships; consequently, ANNs have been successfully applied to predict the deformation behavior of materials under hot working conditions. ANNs can provide a fundamentally different approach to statistical or numerical techniques for materials modelling and materials processing control.

In this study, the high temperature deformation behavior of AISI P20 modified carbon steel subjected to compression tests will be highlighted. From the experimental data obtained, analytical models will be identified on the one hand in order to select the one that could better describe the behavior of this alloy and on the other hand, an ANN model is also developed and a comparative study between the analytical models and the ANN model will follow. A fundamental issue that will also be addressed in this work is the ability to interpolate and extrapolate of the developed models. Indeed, how do models behave when it comes to interpolating or extrapolating data that the model is never aware of ? the answer to this question will be well analyzed in this study.

The main parts of this work are as follows: Section \ref{sec:Materials} presents the material et experimental procedure inverstigated in this study. Section \ref{sec:ConstLaws} is devoted to the presentation of the models developed and their comparative. Section \ref{sec:inExtrapolation} details the validation of interpolation and extrapolation capacity of each model developped. Conclusion and future works are detailed in Section \ref{sec:Conclusion}.

%----------------------------------------------
\section{ Materials and Experiments \label{sec:Materials}}
%----------------------------------------------
%----------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------
The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table \ref{tab:Composition}. Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm. Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$. Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during the tests. The samples were heated up to temperature $1260^\circ$C  and were held for $5$ min to eliminate thermal gradients. Then cooled to test temperature where the specimen is held $1$ minute before deformation. After compression the specimen is quencted rapidly for microstructure studies. The procedure of this test is illustrated in Figure \ref{fig:Heating} where $h_0$ and $R_0$ are the height and radius before compression; $h$, $R_M$, and $R_T$ are respectively the height, big radius and small radius of the specimen after compression.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/Gleeble-3}
\caption{Gleeble 3800 simulator system}
\label{fig:Gleeble3800}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/GleebleDesign}
\caption{Schematic diagram of the experimental process.}
\label{fig:Heating}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
\scalebox{0.9}{
\begin{tabular}{lcccccccc}
\hline
C  &Mn & Mo   & Si   & Ni       &Cr& Cu & Other& Balance\\
\hline
 0.30        &       0.89      &0.52		   &	0.34     &	 0.68          &1.86& 0.17& Microalloying& Iron\\
\hline
\label{tab:Composition}
\end{tabular}}
\end{table}
%------------------------------------------------------------------------
\subsection{Flow stress behavior}
%------------------------------------------------------------------------
The flow stress curves obtained from the compression tests performed on Gleeble-3800 simulator for each test condition are shown in Figure \ref{fig:rawData}. From these curves it can be seen that the flow stress increases with increasing strain rate but decreases with increasing temperature. It should be noted that the strain influences the flow stress. Indeed, for all strain values below $0.2$, the stress increases with strain before reaching a peak value at low strain rates and then decreases to maintain a stable value until the end of the test. The peak stress value increases with strain rate but decreases with temperature. For higher strain rates ($1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$) the flow stress increases throughout the test. The slight increase in stress at low strain rates when the strain is large is due to friction between the specimen and the grip during the test. For low strain rates, lubrication is lost over time and therefore friction occurs. This results in a progressive increase in stress.

To explain the overall behavior of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX). At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening. As the strain continues to increase, the dislocations are set in motion, leading to a stress relaxation phenomenon usually known as DRC. During this DRC mechanism, some of the dislocations are removed, due to their combination with another dislocation, or due to their integration into a grain boundary, and some of them are rearranged and formed as sub-grains within the initial grains. The combination of these dislocations moderates the increase of dislocations linked to strain hardening and thus controls the amount of energy stored in the material and manages the increase in flow stress. DRX consists of the germination of new grains, at the borders or inside the initial grains. These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy. As an example, the Figure \ref{fig:BeforeCompM} and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression. As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate. Indeed, most of the grain boundaries start to form new grains. The identification of the behavioral laws of these curves will be done in the next section in order to predict its behavior in any test condition.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:rawData}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/BeforeCompM}
\caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
\label{fig:BeforeCompM}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/AfterCompM}
\caption{Optical micrograph of AISI P20 alloy after howt compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
\label{fig:AfterCompM}
\end{figure}

%-------------------------------------------------------------------------
\section{Phenomenological constitutive flow laws\label{sec:ConstLaws}}
%-------------------------------------------------------------------------
The complete characterization of the thermomechanical behavior of a material is very important before its use in numerical simulations. This characterization usually involves experimental tests that serve as a basis for the development of constitutive laws. As mentioned in the introduction, many constitutive laws exist today, and selecting one of them based on explicit criteria hinders the development of computational models for new materials. Since the purpose of this work is to compare ANN model to analytical models it is important to justify the choice of the analytical models presented here among the many that exist in the literature. Among the most widely used analytical models nowadays, the Johnson-Cook (JC) model is the most used due to its simplicity of use linked to the number of its reduced and easy to obtain parameters. It should be noted that it is not the best model but the most integrated in finite element software. Hence the existence of several modified forms of this model. The Zerilli-Armstrong model, and particularly its modified form (MZA), is also widely known since it tries to provide solutions to the shortcomings of the JC model, particularly with regard to the coupling of physical parameters. Hence its use also in this study. In this perspective, the Hansel Spittel model (HS)is also one of the most widely used models in numerical simulation of casting and forging operations as it is integrated in the FORGE software. Also, the method of identifying its parameters is very simple to do as it is done in one step. Of course, it has its limitations as will be shown in the following sections. Furthermore, the Arrhenius model will be used in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter Q (the deformation activation energy coefficient) which is of great importance in the study related to the microstructural analysis of materials. The PTM model is also used in this study as it is a model whose formulation does not impose a number of parameters a priori and has proven its ability in our previous work and therefore we want to test it on this type of material as it is formulated to fit any material. 
%-------------------------------------------------------------------------
\subsection{Johnson--Cook model\label{sec:JC}}
%-------------------------------------------------------------------------
The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature . However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature. Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model. Hence its inability to describe the phenomenon of temperature-induced softening. The equation that describes this model is given as follows \cite{johnson1985fracture}:
\begin{equation}
\label{eq: JCmodel}
\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot{\varepsilon}^*\right)\left(1-T^{*^m}\right)
\end{equation}
Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma^y_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent. $C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively. $\mdot{\varepsilon}^*$ is the dimensionless strain rate which is given by $\mdot{\varepsilon}^* = \mdot{\varepsilon^p}/\mdot{\varepsilon_0}$. $\mdot{\varepsilon^p}$ and $\mdot{\varepsilon_0}$ are strain rate and reference strain rate respectively. $T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature (1460$^\circ$C in our case) and reference temperature respectively. For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050^\circ$C respectively and the value of $A$ is $43.0988$ MPa. Here after datailed the steps for determination of the JC model parameters.
At the reference strain rate, Equation \ref{eq: JCmodel} becomes:
\begin{equation}
\label{eq: JCbn}
\sigma^y = A + B\varepsilon^{p^n}
\end{equation}
Taking the natural logarithm on both sides of Equation \ref{eq: JCbn} we have:
\begin{equation}
\label{eq:JClog1}
\ln\left(\sigma^y-A\right)= \ln(B) + n\ln\varepsilon^p
\end{equation}
By plotting $\ln(\sigma^y-A)$ \versus $\ln\varepsilon^p$ (Figure \ref{fig:JCSigmaAB}) from Equation \ref{eq:JClog1}, $n$ and $B$ can be obtained as slope and intercept respectively. Thus, for a strain value equal to $0.1$ the values of these two parameters are $n=0.313969$ and $B=114.518$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/JCSigmaAB}
\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050^\circ$C and $0.1$}
\label{fig:JCSigmaAB}
\end{figure}
\FloatBarrier
Once the parameters $A$, $B$ and $n$ are known and at the reference temperature, the Equation \ref{eq: JCmodel} becomes:
\begin{equation}
\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot{\varepsilon}^*
\end{equation}
From this equation one can easily obtain the parameter $C$ using the linear fitting method for each strain value and averaging all these values as shown in Figure \ref{fig:JCSigmaAB1} the value is $0.0995438$. 
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/JCSigmaAB1}
\caption{Relationship between $\sigma^y/(A+ B\varepsilon^{p^n})$ and $\ln(\dot{\varepsilon}^*)$}
\label{fig:JCSigmaAB1}
\end{figure}
The $m$ parameter is determined at the reference strain rate. Under this condition, the Equation \ref{eq: JCmodel} can be written as following:
\begin{equation}
\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 - T^{*^m}
\end{equation}
Taking the natural logarithm of both sides of that equation, we have:
\begin{equation}
\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)  = m\ln T^*
\end{equation}
Plotting $\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)$ as a function of $\ln T^*$ allows us to get the parameter $m$ as a slope for all values of the deformation by averaging them and the value is $0.898932$. Figure \ref{fig:JCSigmaT} illustrates this determination for some deformations.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.85\columnwidth]
{newFigures/JCSigmaT}
\caption{Relationship between $\ln\left(1 - \sigma^y/\left(A + B\varepsilon^{p^n}\right)\right)$ and $\ln T^*$}
\label{fig:JCSigmaT}
\end{figure}

The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}. The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates. The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates. All parameters of JC model are in Table \ref{tab: JCparameters}.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/CompExpJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model} 
\label{fig:iCorrelationJC}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Johnson-Cook Model}
\scalebox{1.2}{
\begin{tabular}{lccccc}
\hline
&         &             &		   &		  &\\
Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
&         &             &		   &	     &	    \\
\hline
Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
\hline
\label{tab: JCparameters}
\end{tabular}}
\end{table}
%-------------------------------------------------------------------------
\subsection{Modified Zerilli--Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------

As mentioned earlier, Johnson--Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately. Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model \cite{Hull-2011-ITD}. But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} proposed a modified form given by the following equation:  
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009-Thermo-viscoplastic} and determination of its parameters is sumarized as following.

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{tize2022generalized}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
\scalebox{0.83}{
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

%-------------------------------------------------------------------------
\subsection{Hansel and Spittel\label{sec:HSmodel}}
%-------------------------------------------------------------------------
The Hansel-Spittel model is one of the least known models in terms of its  integration in software for finite element simulation although the determination of its parameters is easier than the JC model. A single programming command is sufficient for its identification. However, this model has some difficulties as it loses its accuracy when all parameters are taken into account. For this reason, several authors limit its use to $5$ or $6$ parameters \cite{chadha2018approach, rudnytskyj2020constitutive, el2015comparison}. In this paper the good predictions are with $5$ parameters summarized in Table \ref{tab: HSparameters}. The equation of the model is given by the following relation: 
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/CompExpHS}
\caption{Comparison between the experimental and predicted flow stresses by HS model}
\label{fig:iCorrelationHS}
\end{figure}
\begin{equation}
\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot{\varepsilon}^{p^{m_3}}e^{\frac{m_4}{\varepsilon^p}}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot{\varepsilon}^{p^{m_7T}}T^{m_8}
\end{equation}
